@inproceedings{1547519,
 author = {Li, Xiaolei and Li, Zhenhui and Han, Jiawei and Lee, Jae-Gil},
 title = {Temporal Outlier Detection in Vehicle Traffic Data},
 booktitle = {ICDE '09: Proceedings of the 2009 IEEE International Conference on Data Engineering},
 year = {2009},
 isbn = {978-0-7695-3545-6},
 pages = {1319--1322},
 doi = {http://dx.doi.org/10.1109/ICDE.2009.230},
 publisher = {IEEE Computer Society},
 address = {Washington, DC, USA},
 }

@inproceedings{1547145,
 author = {Lee, Jae-Gil and Han, Jiawei and Li, Xiaolei},
 title = {Trajectory Outlier Detection: A Partition-and-Detect Framework},
 booktitle = {ICDE '08: Proceedings of the 2008 IEEE 24th International Conference on Data Engineering},
 year = {2008},
 isbn = {978-1-4244-1836-7},
 pages = {140--149},
 doi = {http://dx.doi.org/10.1109/ICDE.2008.4497422},
 publisher = {IEEE Computer Society},
 address = {Washington, DC, USA},
 }

@article{1453972,
 author = {Lee, Jae-Gil and Han, Jiawei and Li, Xiaolei and Gonzalez, Hector},
 title = {TraClass: trajectory classification using hierarchical region-based and trajectory-based clustering},
 journal = {Proc. VLDB Endow.},
 volume = {1},
 number = {1},
 year = {2008},
 issn = {2150-8097},
 pages = {1081--1094},
 doi = {http://doi.acm.org/10.1145/1453856.1453972},
 publisher = {VLDB Endowment},
 }

@incollection{Li2007,
    abstract = {Finding hot routes (traffic flow patterns) in a road network is an important problem. They are beneficial to city planners, police departments, real estate developers, and many others. Knowing the hot routes allows the city to better direct traffic or analyze congestion causes. In the past, this problem has largely been addressed with domain knowledge of city. But in recent years, detailed information about vehicles in the road network have become available. With the development and adoption of RFID and other location sensors, an enormous amount of moving object trajectories are being collected and can be used towards finding hot routes. This is a challenging problem due to the complex nature of the data. If objects traveled in organized clusters, it would be straightforward to use a clustering algorithm to find the hot routes. But, in the real world, objects move in unpredictable ways. Variations in speed, time, route, and other factors cause them to travel in rather fleeting  ” clusters.” These properties make the problem difficult for a naive approach. To this end, we propose a new density-based algorithm named FlowScan. Instead of clustering the moving objects, road segments are clustered based on the density of common traffic they share. We implemented FlowScan and tested it under various conditions. Our experiments show that the system is both efficient and effective at discovering hot routes.},
    author = {Li, Xiaolei and Han, Jiawei and Lee, Jae-Gil and Gonzalez, Hector},
    citeulike-article-id = {1580427},
    citeulike-linkout-0 = {http://dx.doi.org/10.1007/978-3-540-73540-3\_25},
    doi = {10.1007/978-3-540-73540-3\_25},
    journal = {Advances in Spatial and Temporal Databases},
    keywords = {location-concepts},
    pages = {441--459},
    posted-at = {2007-08-21 16:29:50},
    priority = {1},
    title = {Traffic Density-Based Discovery of Hot Routes in Road Networks},
    url = {http://dx.doi.org/10.1007/978-3-540-73540-3\_25},
    year = {2007}
}
