\section{Baseline Competitors}

Intro to section; Why do we have baseline competitors, which ones will be introduced, and why those? 

LRU is a competitor, but can not achieve good performance because:
\begin{itemize}	
	\item Has no way to determine the usefulness of adding a path (i.e. no scoring function)
	\item Even if a path P is good (covers many queries), then if a sequence of consequtive queries comes which P can not cover, then it will be evicted.
	\item Has no way to optimize the number of paths in the cache, so available cache space may go unused.
	\item Querying the cache may require a scan of all paths in the cache
\end{itemize}

\section{Contribution} \label{sec:contribution}

Intro to section \\
Show benefits of a static cache over a dynamic cache.\\
List all advantages of a static cache solution \\
(\textit{Static cache} solves goal 2. has zero maintenance cost after filling the cache.)

explain what will be introduced, which sub-problems are considered, and which subsections presents what.


\subsection{Benefit model}
define benefit equations\\
Define optimization goal as a mathematical expfression to be minimized.

\subsection{Hardness Analysis}
Theoretical analysis showing how hard the problem is to solve for \spath caching.\\
show it is NP-Hard
 

\subsection{Greedy algorithm}
shows in more detail how we propose to solve our problem


\subsection{Statistics extration}

\subsubsection{Partition map} 
solves goal 1. reduce time on SP calc as it aids the cache with information on which paths may be useful.\\ 
discussion of kD-Tree.


\subsection{Cache representations and cache concepts} 

\subsubsection{Simple array of paths} - baseline for goal 2, unoptimized and expensive to use.

\subsubsection{Simple array of paths inverted list} - solves goal 2, reduces the query time of the cache.

\subsubsection{Graph representation} - solves goal 1, allows for more paths in cache, which should translate more cache hits.

\subsubsection{Sharing subpaths} - solves goal 1, allows for more paths in cache, translating to more cachehits. Unfortunally has a negative impact on goal 2 as it introduces some overhead in query time.

